---
title: "Reading & Writing Data in R"
author: "YOUR NAME HERE"
date: 'Last rendered on `r format(Sys.time(), "%A, %B %d, %Y @ %I:%M %p")`'
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

```{r}
library(readxl)
library(jsonlite)
```

## RDS and RDATA Files

### Reading and Writing `.rds`

Read an object from an `.rds` file using the following general code. You may need to specify a path name. You can also read data directly from a URL.

```{r, readrds, eval = FALSE}

```

    # syntax
    readRDS(file, 
      refhook = NULL)

Try it!

```{r}

readRDS(file = "data/dcdplyrbabynames.rds")
babynames <- readRDS(file = "data/dcdplyrbabynames.rds")
counties <- readRDS("data/dcdplyrcounties.rds")

```

Save a single object to an `.rds` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder.

```{r, saverds, eval = FALSE}
saveRDS(objectname, file = "my_data.rds")
```

    # syntax
    saveRDS(object, 
      file = "", 
      ascii = FALSE, 
      version = NULL,
      compress = TRUE, 
      refhook = NULL)

Try it!

```{r saveRDS with options}

saveRDS(babynames, file = "data/babynames.rds")

    saveRDS(counties, 
      file = "data/counties.rds", 
      ascii = FALSE, 
      version = NULL,
      compress = TRUE, 
      refhook = NULL)
```

### Reading and Writing `.Rdata`

Load an `.Rdata` file using the following general code. You may need to specify a path name. You can also read data directly from a URL.

```{r, loadrata, eval = FALSE}
load("data.RData")
```

    # syntax
    load(file, 
    envir = parent.frame(), 
    verbose = FALSE)

Try it!

```{r}
load("data/ggplotdiamonds.RData")
load("data/ggplotfish.RData")
load("data/ggplotrecess.RData")
load("data/ggplotiris.RData")
```

Save a one or more objects to an `.Rdata` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder.

```{r, saverdata1, eval = FALSE}
save(objectname, file = "data.RData")
```

```{r, saverdata2, eval = FALSE}
save(objectname1, objectname2, file = "data.RData")
```

    # syntax
    save(..., 
      list = character(),
      file = stop("'file' must be specified"),
      ascii = FALSE, 
      version = NULL, 
      envir = parent.frame(),
      compress = isTRUE(!ascii), 
      compression_level,
      eval.promises = TRUE, 
      precheck = TRUE)

Try it!

```{r}
save(counties, file = "data/counties.RData")
```

Save your entire workspace to an `.Rdata` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder. It can be reloaded with the `load()` function.

```{r, savewkspc, eval = FALSE}
save.image("myworkspace.RData")
```

    # syntax
    save.image(file = ".RData", 
      version = NULL, 
      ascii = FALSE,
      compress = !ascii, 
      safe = TRUE)

Try it!

```{r}
save.image("myworkspace2021Oct14.RData")
```

```{r}
load("myworkspace2021Oct14.RData")
```
## Excel Files

Use `library(readxl)` at beginning of script.

```{r, readxl}
excel_sheets("data/powerball.xlsx") # returns names of sheets
excel_format("data/powerball.xlsx") # returns .xls or .xlsx

read_excel("data/powerball.xlsx", sheet = 1) # select sheet by number ...
read_excel("data/powerball.xlsx", sheet = "Inflation") # ... or by name
```
```{r, readxl, a much messier spreadsheet}

```
## JSON Files

TBA